\chptr{Networks in a Nutshell}
\marginpar{\minitoc}

This chapter covers key concepts regarding networks which
are essential to understand many of the topics of this
course. We assume that the reader is already familiar
with basic ideas encountered in previous networking classes.
However, this chapter aims at refreshing those memories,
particularly the ones concerning the most important computer
network: the Internet.


\section{The state of the Internet}
Given the unprecedented growth of technology in the
last few decades, new challenges arise: how do we
connect billions of mobile devices to the Internet
and among each other? Can we improve safety in streets
by deploying ad-hoc car networks? How can we handle
hundreds of devices in an IoT network? Can we bring
connectivity to uncovered (and poorer) communities
in a cost-effective manner?

Along with these new issues, something weird has
been happening lately: much of the traffic that
fills the Internet and other computer networks
involves machine-to-machine (M2M) communications.


\section{The TCP/IP model}

\subsection{Application}

\subsection{Transport}

\subsection{Network}

\subsection{Link}

\subsection{Physical and other layers}


\section{How to...}
This section deals with some of the mechanisms and protocols which
enable a host to connect to another machine.

\subsection{Connect to a network and DHCP}

\subsection{Communicate within a network and ARP}

\subsection{Communicate outside a LAN and routing}


\section{Wireless networks}
\section{Performance}